Coupled response of stomatal and mesophyll conductance to light enhances photosynthesis of shade leaves under sunflecks.

### 2016-06-23 gm_newphyt/manuscript_gmes.Rmd
Minor edits and reference for multcomp

\
Leaf gas exchange measurements were initiated in October 2013 when trees had both ample height growth and canopy development for realistic canopy light gradients to be measured. At this point, trees under AT treatment had a mean diameter of 28.2&pm;1.1 mm **SD, SE or CI?**, height of 348&pm;15.1 cm and an leaf area of 3.9&pm;0.1 m^2^. For ET treatments, trees had a mean diameter of 34.1&pm;2.1 mm, height of 418.3&pm;23.1 cm and an leaf area of 6.2&pm;0.2 m^2^. Leaf area was calculated based on complete leaf counts and mean leaf size from a subsample [@drake2016does].

@@

##Data analysis
Differences in respones of dependent variables to either the warming treatment or leaf type were analysed with linear mixed-effects models with WTC as a random effect, and leaf type (sun, shade or shade in the sun) and warming treatment as fixed effects **(and the interaction??)**. Explained variance (R^2^) of mixed models were computed as in Nakagawa & Schielzeth [-@nakagawa2013general], in which the marginal R^2^ represents variance explained by fixed factors and the conditional R^2^ by both fixed and random factors. Confidence intervals (95 %) of mixed effect linear models were generated using bootstrapping methods with 999 simulations, using the bootMer function in the 'lme4' package [@bates2013lme4]. For non-linear relationships, confidence intervals were estimated by fitting a generalized additive model to the data with the 'mgcv' package [@wood2006], using WTC as a random effect. All tests of statistical significance were conducted at an $\alpha$ of 0.05. All analyses were performed with R 3.3.0 [@RDevelopmentCoreTeam2011].

@@

##Leaf resource distribution
Across six measurement campaigns over the 7 month period, PPFD was reduced on average by >75% in the shade (Figure `r parfig`). Leaf-specific hydraulic conductance (*K*~L~) was similar across sun and shade leaves (Table `r wtc3tab1`). This was because neither leaf water potentials ($\Psi_{pd}$ and $\Psi_L$, Table `r wtc3tab1`) nor transpiration rates (E, Table `r wtc3tab2`) differed between leaf types. Leaf *N*~a~ was approximately 20% higher in sun leaves compared to shade leaves (Table `r wtc3tab1`). Leaf mass per area (LMA) was not different between leaf types (Table `r wtc3tab1`). No effect of the warming treatment **was interaction tested??** was detected with  PPFD, $\Psi_{pd}$, $\Psi_L$, *K*~L~, *E*~L~, *N*~a~ or LMA either within or across leaf types (P > 0.05).

@@

```{r par, fig.width=7, fig.height=7, echo=FALSE,warning=FALSE,dev="png",message=FALSE, dpi=600, dev.args=list(type="cairo"), eval=includeFigs}
source("master_scripts/par2.R")
```  
\
**Figure 1**. Environmental conditions during the six measurement campaigns. Bars represent the local light environment for sun and shade leaves during six gas exchange campaigns from October 2013 to April 2014 (as photosynthetic photon flux density, PPFD). Means &pm; 1 standard error represent PPFD measured with a ceptometer at the height of each selected leaf in the canopy. Points connected by a line represent the mean (&pm; 1 standard error) daily maximum air temperature during each campaign period. Each date represents the starting date for each measurement campaign; each campaign was completed in **how many days???*.

>>>>

\
Leaf gas exchange measurements were initiated in October 2013 when trees had both ample height growth and canopy development for realistic canopy light gradients to be measured. At this point, trees under AT treatment had a mean diameter of 28.2&pm;1.1 mm (SE), height of 348&pm;15.1 cm and an leaf area of 3.9&pm;0.1 m^2^. For ET treatments, trees had a mean diameter of 34.1&pm;2.1 mm, height of 418.3&pm;23.1 cm and an leaf area of 6.2&pm;0.2 m^2^. Leaf area was calculated based on complete leaf counts and mean leaf size from a subsample [@drake2016does].

@@

##Data analysis
Differences in respones of dependent variables to either the warming treatment or leaf type were analysed with linear mixed-effects models with WTC as a random effect, and leaf type (sun, shade or shade in the sun) and warming treatment, and the interaction as fixed effects. The interaction was never significant, so we only report results of the tests of the main effects. Explained variance (R^2^) of mixed models were computed as in Nakagawa & Schielzeth [-@nakagawa2013general], in which the marginal R^2^ represents variance explained by fixed factors and the conditional R^2^ by both fixed and random factors. Confidence intervals (95 %) of mixed effect linear models were generated using bootstrapping methods with 999 simulations, using the bootMer function in the 'lme4' package [@bates2013lme4]. For non-linear relationships, confidence intervals were estimated by fitting a generalized additive model to the data with the 'mgcv' package [@wood2006], using WTC as a random effect. All tests of statistical significance were conducted at an $\alpha$ of 0.05. For multiple post-hoc comparisons, we used Tukey pairwise comparison tests with the 'multcomp' package [@hothorn2008]. In all results, we report the mean &pm; one standard error for the mean (SE). All analyses were performed with R 3.3.0 [@RDevelopmentCoreTeam2011].

@@

##Leaf resource distribution
Across six measurement campaigns over the 7 month period, PPFD was reduced on average by >75% in the shade (Figure `r parfig`). Leaf-specific hydraulic conductance (*K*~L~) was similar across sun and shade leaves (Table `r wtc3tab1`). This was because neither leaf water potentials ($\Psi_{pd}$ and $\Psi_L$, Table `r wtc3tab1`) nor transpiration rates (E, Table `r wtc3tab2`) differed between leaf types. Leaf *N*~a~ was approximately 20% higher in sun leaves compared to shade leaves (Table `r wtc3tab1`). Leaf mass per area (LMA) was not different between leaf types (Table `r wtc3tab1`). No effect of the warming treatment was detected with  PPFD, $\Psi_{pd}$, $\Psi_L$, *K*~L~, *E*~L~, *N*~a~ or LMA either within or across leaf types (P > 0.05).

@@

```{r par, fig.width=7, fig.height=7, echo=FALSE,warning=FALSE,dev="png",message=FALSE, dpi=600, dev.args=list(type="cairo"), eval=includeFigs}
source("master_scripts/par2.R")
```  
\
**Figure 1**. Environmental conditions during the six measurement campaigns. Bars represent the local light environment for sun and shade leaves during six gas exchange campaigns from October 2013 to April 2014 (as photosynthetic photon flux density, PPFD). Means &pm; 1 standard error represent PPFD measured with a ceptometer at the height of each selected leaf in the canopy. Points connected by a line represent the mean (&pm; 1 standard error) daily maximum air temperature during each campaign period. Each date represents the starting date for each measurement campaign; each campaign was completed in 3 days (**Check this- one or two took longer than this?**).
